### 2023-03-06 manuscript.tex
* manuscript.tex: Fix wording.

Strictly local logical tranductions, as shown thus far, satisfy both
first-orderness and quantifier-freeness.  This is not a coincidence,
but rather the expected outcome.  By disallowing quantification,
logical formulae are allowed to refer to terms other than the bounded
ones only by the means of the predecessor and successor functions,
which in turn allude to the notion of locality.

>>>>

Strictly local logical tranductions, as shown thus far, satisfy both
first-orderness and quantifier-freeness.  This is not a coincidence,
but rather the expected outcome.  By disallowing quantification,
logical formulae are allowed to refer to terms other than the input
terms only by the means of the predecessor and successor functions,
which in turn allude to the notion of locality.
